Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2015-12-21 ijar-npb-ms.tex
text for bridge system example, breaking system example

As a toy example, consider a `bridge' type system layout with three types of components T1, T2 and T3,
as depicted in Figure~\ref{fig:bridge-layout}.
For components type T1 and T2, we consider a near-noninformative set of prior reliability functions.
For components of type T3, we consider an informative set of prior reliability functions
as given in Table~\ref{tab:bridge-T3prior}.
This set could result from eliciting prior functioning probabilities at times $0,1,2,3,4,5$ only,
and filling up the rest.
These prior assumptions, together with sets of posterior reliability functions
resulting from three different scenarios for test data for component type T3,
are illustrated in Figures~\ref{fig:bridge-fitting}, \ref{fig:bridge-early} and \ref{fig:bridge-late}; 
test data for components of type T1 and T2 are invariably
$\vec{t}^1 = (2.0, 2.2, 2.4, 2.6)$ and $\vec{t}^2 = (3.0, 3.2, 3.4, 3.6)$, respectively.

@@

In Figure~\ref{fig:bridge-fitting}, 
test data for component type T3 is $\vec{t}^3 = (0.5, 1.5, 2.5, 3.5)$,
and so in line with expectations.
The posterior set of reliability functions for each component type and the whole system
is considerably smaller as compared to the prior set
(due to the low prior strength intervals
$[\ntzl{1},\ntzu{1}] = [\ntzl{2},\ntzu{2}] = [1,2]$, $[\ntzl{3},\ntzu{3}] = [1,4]$)
and so giving more precise reliability statements.
We see that posterior lower and upper functioning probabilities drop at those times $t$
when there is a failure time in the test data,
or a drop in the prior functioning probability bounds.
Note that the lower bound for prior system reliability function is zero
due to the prior lower bound for T1;
for the system to function, the component of type T1 must function.

@@

In Figure~\ref{fig:bridge-early},
test data of component type T3 is instead $\vec{t}^3 = (0.6, 0.7, 0.8, 0.9)$,
and so earlier than expected.

@@

In Figure~\ref{fig:bridge-late}, 
test data of component type T3 is now $\vec{t}^3 = (4.1, 4.2, 4.3, 4.4)$,
and so later than expected.

@@

***calculate and show $\Rsys(t)$ plots for a range of examples (keep system layout fixed?):
informative prior set for some component types, different degree of imprecision,
noninformative prior set for other components (make clear that precise `noninformative' prior actually contains info), 
combine with prior-data conflict and non-conflict test data,
to show effect of precision of prior knowledge / amount of data / (degree of) prior-data conflict on $\Rsys(t)$.***

***Vacuous prior sets $[\yktzl, \yktzu] = (0,1)$ for some component types,
informative prior sets for others. $[\nktzl, \nktzu]$ interval for all component types.***

>>>>

As a toy example, consider a `bridge' type system layout with three types of components T1, T2 and T3,
as depicted in Figure~\ref{fig:bridge-layout}.
For component types T1 and T2, we consider a near-noninformative set of prior reliability functions.
For components of type T3, we consider an informative set of prior reliability functions
as given in Table~\ref{tab:bridge-T3prior}.
This set could result from eliciting prior functioning probabilities at times $0,1,2,3,4,5$ only,
and filling up the rest.
These prior assumptions, together with sets of posterior reliability functions
resulting from three different scenarios for test data for component type T3,
are illustrated in Figures~\ref{fig:bridge-fitting}, \ref{fig:bridge-early} and \ref{fig:bridge-late}; 
test data for components of type T1 and T2 are invariably taken as
$\vec{t}^1 = (2.0, 2.2, 2.4, 2.6)$ and $\vec{t}^2 = (3.0, 3.2, 3.4, 3.6)$, respectively.

@@

In Figure~\ref{fig:bridge-fitting}, 
test data for component type T3 is $\vec{t}^3 = (0.5, 1.5, 2.5, 3.5)$,
and so in line with expectations.
The posterior set of reliability functions for each component type and the whole system
is considerably smaller as compared to the prior set
(due to the low prior strength intervals
$[\ntzl{1},\ntzu{1}] = [\ntzl{2},\ntzu{2}] = [1,2]$, $[\ntzl{3},\ntzu{3}] = [1,4]$)
and so giving more precise reliability statements.
We see that posterior lower and upper functioning probabilities drop at those times $t$
when there is a failure time in the test data,
or a drop in the prior functioning probability bounds.
Note that the lower bound for prior system reliability function is zero
due to the prior lower bound of zero for T1;
for the system to function, the component of type T1 must function.

@@

In Figure~\ref{fig:bridge-early},
test data of component type T3 is instead $\vec{t}^3 = (0.6, 0.7, 0.8, 0.9)$,
and so earlier than expected.
Compared to Figure~\ref{fig:bridge-fitting},
posterior functioning intervals for T3 are wider between $t=1$ and $t=3.5$,
reflecting additional imprecision due to prior-data conflict.
For $t > 1$, it is clearly visible how $\ytnu{3}$ is halfway between $\ytzu{3}$ and $s_t^3/n_3 = 0$
(weights $\ntzu{3} = 4$ and $n_3 = 4$),
while $\ytnl{3}$ is one-fifth of $\ytzl{3}$
(weights $\ntzl{3} = 1$ and $n_3 = 4$).
Note that the posterior system functioning probability is constant for $t \in [1,2]$
because the prior functioning probability is constant for $t \in [1,2]$
and there are no failure times $\in [1,2]$ in the test data.

@@

In Figure~\ref{fig:bridge-late}, 
test data of component type T3 is now $\vec{t}^3 = (4.1, 4.2, 4.3, 4.4)$,
and so observed failures are later than expected.
Here we see that for $t \in [2,4]$,
posterior functioning bounds for T3 are even wider than prior functioning bounds.
The width turns back to being half the prior width
only after the four failures.
The imprecision carries over to the system bounds,
where we see wider bounds as compared to the other scenarios
especially between $t=2$ and $t=4$.

@@

***Another example: simplified automotive breaking system, Figure~\ref{fig:breakingsystem}.
Prior sets and data exemplary only, prior bounds more smooth curves?
The master breaking cylinder (M) activates all four wheel braking cylinders (C1 -- C4),
which in turn actuate a braking pad assembly each (P1 -- P4).
The hand break mechanism (H) goes directly to two brake pad assemblies P3 and P4;
the car breaks when at least one brake pad assembly is actuated.***

\begin{figure}
\includegraphics[width=\textwidth]{breakingsystem-1}
\caption{A simplified automotive breaking system. ***System layout goes to empty space in lower row.}
\label{fig:breakingsystem}
\end{figure}

%***calculate and show $\Rsys(t)$ plots for a range of examples (keep system layout fixed?):
%informative prior set for some component types, different degree of imprecision,
%noninformative prior set for other components (make clear that precise `noninformative' prior actually contains info), 
%combine with prior-data conflict and non-conflict test data,
%to show effect of precision of prior knowledge / amount of data / (degree of) prior-data conflict on $\Rsys(t)$.***

%***Vacuous prior sets $[\yktzl, \yktzu] = (0,1)$ for some component types,
%informative prior sets for others. $[\nktzl, \nktzu]$ interval for all component types.***
